Fifteen years of decentralization attempts

### 2014-03-20 paper.tex

	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of anonymous systems\footnote{Found at https://github.com/redecentralize/alternative-internet}. For each of the listed systems, we have created an entry in a table that shows the total lines of code (LOC), activity, amount of contributors, (main) programming language, amount of commits, etc. This table is available on the same Github page. We hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained. This Github project, including the table, is publicly available.

>>>>

	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of these systems maintained by redecentralize.org\footnote{Found at https://github.com/redecentralize/alternative-internet}. For each of the listed systems, we have created an entry in a table that shows statistics such as the total lines of code (LOC), activity, amount of contributors, (main) programming language and amount of commits, sourced from Ohloh. This table is available on the same Github repository. We hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained. This Github repository, including the table, is publicly available.
